The Efficient Handling of Guards in the Design of RPython's Tracing JIT

### 2012-08-13 talk/vmil2012/paper.tex
hide Appendix

After optimization the resulting trace is handed over to the platform specific
backend to be compiled to machine code. The compilation phase consists of two
passes over the lists of instructions, a backwards pass to calculate live
ranges of IR-level variables and a forward pass to emit the instructions. During
the forward pass IR-level variables are assigned to registers and stack
locations by the register allocator according to the requirements of the
emitted instructions.  Eviction/spilling is performed based on the live range
information collected in the first pass. Each IR instruction is transformed
into one or more machine level instructions that implement the required
semantics. Operations without side effects whose result is not used are not
emitted. Guards instructions are transformed into fast checks at the machine
code level that verify the corresponding condition.  In cases the value being
checked by the guard is not used anywhere else the guard and the operation
producing the value can often be merged, further reducing the overhead of the guard.
Figure \ref{fig:trace-compiled} shows how the \texttt{int\_eq} operation
followed by a \texttt{guard_false} from the trace in Figure~\ref{fig:trace-log} are compiled to
pseudo-assembler if the operation and the guard are compiled separated or if
they are merged.

@@

\section*{Appendix}
\todo{remove this section and the figures}
\begin{figure*}
    \include{figures/ops_count_table}
    \caption{Relative numbers of operations in the traces generated for
    different benchmarks}
    \label{fig:ops_count}
\end{figure*}
\begin{figure*}
\centering
\includegraphics[width=\textwidth]{figures/ops_pie.pdf}
\caption{Relative frequency of operations before and after optimization}
\label{fig:ops_pie}
\end{figure*}
\bibliographystyle{abbrv}
\bibliography{zotero,paper}
\listoftodos
\end{document}

>>>>

After optimization the resulting trace is handed over to the platform specific
backend to be compiled to machine code. The compilation phase consists of two
passes over the lists of instructions, a backwards pass to calculate live
ranges of IR-level variables and a forward pass to emit the instructions. During
the forward pass IR-level variables are assigned to registers and stack
locations by the register allocator according to the requirements of the
emitted instructions.  Eviction/spilling is performed based on the live range
information collected in the first pass. Each IR instruction is transformed
into one or more machine level instructions that implement the required
semantics. Operations without side effects whose result is not used are not
emitted. Guards instructions are transformed into fast checks at the machine
code level that verify the corresponding condition.  In cases the value being
checked by the guard is not used anywhere else the guard and the operation
producing the value can often be merged, further reducing the overhead of the guard.
Figure \ref{fig:trace-compiled} shows how the \texttt{int\_eq} operation
followed by a \texttt{guard\_false} from the trace in Figure~\ref{fig:trace-log} are compiled to
pseudo-assembler if the operation and the guard are compiled separated or if
they are merged.

@@

%\section*{Appendix}
%\todo{remove this section and the figures}
%\begin{figure*}
%    \include{figures/ops_count_table}
%    \caption{Relative numbers of operations in the traces generated for
%    different benchmarks}
%    \label{fig:ops_count}
%\end{figure*}
%\begin{figure*}
%\centering
%\includegraphics[width=\textwidth]{figures/ops_pie.pdf}
%\caption{Relative frequency of operations before and after optimization}
%\label{fig:ops_pie}
%\end{figure*}
\bibliographystyle{abbrv}
\bibliography{zotero,paper}
\listoftodos
\end{document}
